---
output: html_document
editor_options: 
  chunk_output_type: console
---


## `r envir$dset_name` {.tabset .tabset-fade .tabset-pills}

```{r, include = FALSE}
with(envir, {
if (dset_name %in% c('Achilles RNAi', 'DRIVE RNAi', 'Comb RNAi', 'CRISPR')) {
  target_info <- gene_info %>%
   left_join(df_90_rank[[dset_name]], by = 'Gene')
  if (dset_name %in% names(biomarker_info)) {
   target_info %<>% left_join(biomarker_info[[dset_name]], by = 'Gene')
  }
  if(dset_name %in% names(gene_stats)) {
    target_info %<>% left_join(gene_stats[[dset_name]], by = target_type)
  }
} else if (dset_name == 'PRISM') {
  target_info <- PRISM_cmpd_info %>%
   left_join(df_90_rank[[dset_name]], by = target_type)
} else if (dset_name == 'GDSC') {
  target_info <- GDSC_cmpd_info %>%
   left_join(df_90_rank[[dset_name]], by = target_type)
} else if (dset_name == 'CTD2') {
  target_info <- CTD2_cmpd_info %>%
   left_join(df_90_rank[[dset_name]], by = target_type)
}

res <- cdsr:::make_pref_dep_table(pref_dep_stats[[dset_name]], 
                                  target_info, 
                                  target_type, 
                                  test_dir, 
                                  max_pref_deps, 
                                  min_show_top_deps,
                                  q_thresh)
if ('normLRT' %in% colnames(target_info)) {
  res_normLRT <- cdsr:::make_pref_dep_table(pref_dep_stats[[dset_name]], 
                                  target_info, 
                                  target_type, 
                                  test_dir, 
                                  max_pref_deps, 
                                  min_show_top_deps,
                                  q_thresh = Inf,
                                  normLRT_thresh = normLRT_thresh)
} else {
  res_normLRT <- NULL
}
})
```

### Preferential dependency table 

```{r}
with(envir, {
if (target_type == 'Gene') {
  tname <- target_type
} else {
  tname <- 'Compound'
}
})

```

**Found `r envir$res$n_pref_deps` `r envir$tname`s at q-value threshold of `r envir$q_thresh`**

Showing top `r envir$res$n_rows_used` `r envir$tname`s

Preferential dependencies are defined based on the mean difference between in-group and out-group CLs. Genes with significant mean-difference, and where in-group CLs are more dependent than out-group CLs are defined as preferential dependencies. Significance is assessed using empirical-Bayes moderated t-statistics (via the software package Limma). Q-values of `r envir$q_thresh` are considered significant.

```{r}
envir$res$tab
```

### normLRT dependency table 

This table shows genes with normLRT scores > `r envir$normLRT_thresh`.

```{r}
envir$res_normLRT$tab
```


```{r, include = FALSE}
with(envir, {
cur_stats <- pref_dep_stats[[dset_name]] %>% 
  left_join(target_info, by = target_type)
if (test_dir == 'both') {
    cur_stats %<>% mutate(esize = abs(EffectSize))
  } else if (test_dir == 'left') {
    cur_stats %<>% mutate(esize = -EffectSize)
  } else {
    cur_stats %<>% mutate(esize = EffectSize)
  }
if (target_type == 'broad_id') {
  cur_stats %<>% mutate(broad_id = pert_iname) %>% 
    dplyr::rename(Compound = broad_id)
} else if (target_type == 'DRUG ID') {
  cur_stats %<>% mutate(`DRUG ID` = `DRUG NAME`) %>% 
    dplyr::rename(Compound = `DRUG ID`)
} else if (target_type == 'master_cpd_id') {
  cur_stats %<>% mutate(master_cpd_id = cpd_name) %>% 
    dplyr::rename(Compound = master_cpd_id)
}
})
```

### Volcano plot
Showing strength and significance of two-group comparison for each gene. Genes with drugs (according to Integrity database) are highlighted by color

```{r, fig.width = 8, fig.height=6}
with(envir, cdsr:::make_volcano_plot(cur_stats, test_dir, n_targ_label = n_targ_label, target_type = target_type, q_thresh = q_thresh))
```

### Distribution of cell line features by lineage

```{r, fig.width = 7, fig.height = 5}
with(envir, {
  df <- dat$sample_info %>% 
  filter(CCLE_ID %in% common_CLs) %>% 
  left_join(data.frame(CCLE_ID = names(CL_var), CL_var = CL_var), by = 'CCLE_ID')
lin_ord <- df %>% filter(!is.na(lineage)) %>% dplyr::group_by(lineage) %>% dplyr::summarise(n = n()) %>% dplyr::arrange(dplyr::desc(n)) %>% .[['lineage']]
df %<>% mutate(lineage = factor(lineage, levels = lin_ord))

if (length(unique(CL_var[!is.na(CL_var)])) == 2) {
  ggplot(df %>% filter(!is.na(lineage)), 
         aes(x = lineage, fill = CL_var)) + 
    geom_histogram(stat = 'count') +
    cdsr:::theme_Publication() +
    cdsr:::scale_fill_Publication() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
} else {
  ggplot(df %>% filter(!is.na(lineage)),
         aes(x = lineage, y = CL_var)) + 
    geom_boxplot(alpha = 0.5, outlier.shape = NA) +
    geom_jitter(alpha = 0.5, size = 1, width = 0.1) +
    cdsr:::theme_Publication() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
}
})
```

### Pref-vs-LRT

```{r, fig.width = 8, fig.height=6}
with(envir, {
if (target_type %in% c('broad_id', 'DRUG ID', 'master_cpd_id')) {
  cur_target_type <- 'Compound'
} else {
  cur_target_type <- target_type
}
  if ('normLRT' %in% colnames(cur_stats)) {
ggplot(cur_stats, aes(EffectSize, normLRT)) + 
  geom_point(aes(color = q_val < q_thresh), alpha = 0.75) + 
  geom_hline(yintercept = normLRT_thresh, linetype = 'dashed') +
  geom_text_repel(data = cur_stats %>% 
                    filter(normLRT > normLRT_thresh) %>% 
                    arrange(dplyr::desc(esize)) %>% 
                    head(n_targ_label),
                  aes_string('label' = cur_target_type),
                  size = 3) +
  ylab('normLRT')  +
  guides(color = guide_legend(title = 'sig')) +
  cdsr:::theme_Publication() +
  cdsr:::scale_colour_Publication()
  }
})
```


### Pref-vs-common essentiality

```{r, fig.width = 8, fig.height=6}
with(envir, {
if (target_type %in% c('broad_id', 'DRUG ID', 'master_cpd_id')) {
  cur_target_type <- 'Compound'
} else {
  cur_target_type <- target_type
}
ggplot(cur_stats, aes(EffectSize, deprank_90perc)) + 
  geom_point(aes(color = q_val < q_thresh), alpha = 0.75) + 
  geom_hline(yintercept = 0.2, linetype = 'dashed') +
  geom_text_repel(data = cur_stats %>% 
                    arrange(dplyr::desc(esize)) %>% 
                    head(n_targ_label),
                  aes_string('label' = cur_target_type),
                  size = 3) +
  ylab('90th percentile dependency rank')  +
  guides(color = guide_legend(title = 'sig')) +
  cdsr:::theme_Publication() +
  cdsr:::scale_colour_Publication() 
})
```

```{r, fig.width = 8, fig.height=6}
with(envir, {
if (target_type %in% c('broad_id', 'DRUG ID', 'master_cpd_id')) {
  cur_target_type <- 'Compound'
} else {
  cur_target_type <- target_type
}
if ('frac_FDR_deps' %in% colnames(cur_stats)) {
  ggplot(cur_stats, aes(EffectSize, frac_FDR_deps)) + 
    geom_jitter(aes(color = q_val < q_thresh), alpha = 0.75, width = 0, height = 0.01) + 
    geom_hline(yintercept = 0.2, linetype = 'dashed') +
    geom_text_repel(data = cur_stats %>% 
                      arrange(dplyr::desc(esize)) %>% 
                      head(n_targ_label),
                    aes_string('label' = cur_target_type),
                    size = 3) +
    ylab('Fraction CLs dependent')  +
    guides(color = guide_legend(title = 'sig')) +
    cdsr:::theme_Publication() +
    cdsr:::scale_colour_Publication() 
}
})
```



### Pref-vs-biomarker

```{r, fig.width = 8, fig.height=6}
with(envir, {
if ('overall_auc' %in% colnames(cur_stats)) {
ggplot(cur_stats, aes(EffectSize, overall_auc)) + 
  geom_point(aes(color = q_val < q_thresh), alpha = 0.75) + 
  geom_hline(yintercept = biomarker_auc_thresh, linetype = 'dashed') +
  geom_text_repel(data = cur_stats %>% 
                    arrange(dplyr::desc(esize)) %>% 
                    head(n_targ_label),
                  aes_string('label' = cur_target_type),
                  size = 3) +
  ylab('Predictive model AUC')  +
  guides(color = guide_legend(title = 'sig')) +
  cdsr:::theme_Publication() +
  cdsr:::scale_colour_Publication()
}
})
```


### Top Co-dependency clusters
Graph visualization of dependency-correlations among top `r envir$n_codep_genes` dependencies. Edges are shown between genes with significant correlation. Node size indicates the strength of preferential dependency (mean diff). Colors show dependency groups identified by community detection algorithm

```{r, fig.width = 10, fig.height = 10}
with(envir, {
  top_gene_stats <- pref_dep_stats[[dset_name]] %>%
  arrange(q_val) %>%
  head(n_codep_genes)
# top_gene_stats$target <- top_gene_stats[[target_type]]
if (dset_name %in% c('PRISM', 'GDSC', 'CTD2')) {
  top_gene_stats %<>% left_join(target_info, by = target_type) 
}
cdsr:::make_network_target_vis(top_gene_stats, cur_dep_mat, target_type = target_type)
})
```

### GSA {.tabset .tabset-fade}

```{r}
with(envir, {
if (target_type == 'broad_id') {
  target_gs <- c('Rep_moa', 'Rep_target')
} else if (target_type == 'DRUG ID') {
    target_gs <- c('GDSC_target', 'GDSC_target_pathway')
} else if (target_type == 'master_cpd_id') {
    target_gs <- c('CTD2_target', 'CTD2_moa')
} else {
  target_gs <- used_gscs
}
})
```

```{r, include = FALSE}
with(envir, {
  gsea_res <- list()
  all_genes <- list()
  X <- cur_dep_mat[common_CLs,]
  Y <- CL_var[common_CLs]
  if (!is.null(covars)) {
    #project covars from each column of X and from Y
     Z <- covars[common_CLs]
     if (is.vector(Z)) {
         Z <- data.frame(matrix(Z, ncol=1))
        colnames(Z) <- 'cov'
     }
     Z <- model.matrix(as.formula(paste0('~0 + ', paste(colnames(Z), collapse = '+'))), Z)
    if (nproc > 0) {
      library(plyr)
      library(doMC)
      doMC::registerDoMC(cores=nproc)
      X <- plyr::aaply(X, 2, function(col) {
        ncol <- rep(NA, length(col))
        ncol[!is.na(col)] <- resid(lm(col ~ Z))
        return(ncol)
      }, .parallel=TRUE) %>% t()
    } else {
      X <- apply(X, 2, function(col) {
        ncol <- rep(NA, length(col))
        ncol[!is.na(col)] <- resid(lm(col ~ Z))
        return(ncol)
      })
    }
    Y <- resid(lm(Y ~ Z))
  }
  for (gs_name in target_gs) {
    if (!is.null(pref_dep_stats[[dset_name]])) {
      print(gs_name)
      invisible(gsea_res[[gs_name]] <- cdsr:::get_gsea_results(
                                                    X, 
                                                    Y, 
                                                    gsc = gsc_data[[gs_name]], 
                                                    covars = NULL, 
                                                    test_dir,
                                                    target_type))
      if (rank_gs_by_NES) {
        gsea_res[[gs_name]] %<>% 
          filter(q_val < q_thresh) %>% 
          arrange(dplyr::desc(norm_enrich_stat))
      }
    }
    all_genes[[gs_name]] <- pref_dep_stats[[dset_name]][[target_type]]
    if (target_type == 'broad_id') {
      all_genes[[gs_name]] %<>% str_sub(1,13) %>% make.names()
    } else if (target_type == 'DRUG ID') {
      all_genes[[gs_name]] <-  paste0("ID", all_genes[[gs_name]])
    }
  }
})
```

```{r, include = FALSE}
cur_out <- NULL
for (gs_name in envir$target_gs) {
  envir$gs_name <- gs_name
  cur_out <- c(cur_out, knit_child(system.file("rmd/depCon_gs_template.Rmd", package="cdsr"), envir = envir))
}
```

`r paste(cur_out, collapse='\n')`

